Optimal Sizing of Stand-alone Solar PV Systems Through Automated Formal Synthesis Method

### 2019-09-24 Tex/IEEE_TOSE/trindade_IEEETOSE_rev0.tex
updated Section IV.D
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

Comparing the results between the formal synthesis with CPAchecker and HOMER Pro  (cf.~\textit{EQ2}), we observed that most results are quite similar, in terms of technical solution and cost (cf. Table~\ref{tab1}). Particularly related to LCC, the cost was very close in cases 
$1$, $4$, $5$ and $6$, with difference varying from $0.23$\% to $17.4$\%. 
Even adopting the same price per kW to the PV panels, 
inverters, and batteries, HOMER Pro does not use costs 
related to charge controllers, which were introduced into the 
CPAchecker modeling. The premise used in CPAchecker to adopt 
a fixed annual cost for operation and maintenance can produce 
some impact as well at this discrepancy; however, it is not significant
since this annual cost is too small when compared to the resulting LCC value.

However, there exists a huge divergence in case study $2$, where the costs presented by HOMER Pro were $54$\% higher than our automated synthesis tool, probably because the operation and maintenance costs assumed by our automated synthesis tool were underestimated to that specific load.

>>>>

Comparing the results between the formal synthesis with CPAchecker and HOMER Pro (cf.~\textit{EQ2}), 
we observed that most results are quite similar, in terms of technical solution and cost (cf. Table~\ref{tab1}). 
Mainly related to LCC, the cost was very close in cases $1$, $4$, $5$ and $6$, with difference varying from $0.23$\% to $17.4$\%. 
Even adopting the same price per kW to the PV panels, 
inverters, and batteries, HOMER Pro does not use costs 
related to charge controllers, which we introduced into the 
CPAchecker modeling. The premise used in CPAchecker to adopt 
a fixed annual cost for operation and maintenance can produce 
some impact as well at this discrepancy; however, it is not significant
since this annual cost is too small when compared to the resulting LCC value.
However, there exists a considerable divergence in case study $2$, where the costs presented by HOMER Pro were $54$\% higher than our automated synthesis tool, probably because we underestimated the operation and maintenance costs assumed by our automated synthesis tool to that specific load.
